A practical look at genetic algorithms

### 2015-11-22 evolutionaryComputation/practicals/report.tex
running all tests

\subsubsection{Only create children if the genes are new}
If the genes are new then create the children otherwise return the parent.
\section{Execution}
%TODO:
% 1. Experiments
% Use stoastic within the algoritm
%	Draw a graph from the experiments
%		* pop size on x, # succes on Y
% maybe some more testing of the crossovers?
% also try to implement a threading scheme??

>>>>

\subsubsection{Only create children if the genes are new}
If the genes are new then create the children otherwise return the parent.
This reduces evaluations and object creations. Its becomes more effective
at deeper generation, it even slows down the fastest GA's by a few miliseconds
but the deeper GA are lots faster.

This can be done safely because strings are immutable and so are the members.
So I can reuse them whenever its needed.

To reduce the amount of string comparisons, first the hascode function is called
This will cache itself, I know this because I inspected the source code of the
String class in Java.
\section{Execution}
%TODO:
% 1. Experiments
% Use stoastic within the algoritm
%	Draw a graph from the experiments
%		* pop size on x, # succes on Y
% maybe some more testing of the crossovers?
% also try to implement a threading scheme??
